---
title: "Introduction"
output: html_document
author: "Your Name"
date: "1-21-2020"
editor_options: 
  chunk_output_type: console
---

# Main Ideas

- R is a statistical programming language
- RStudio is a convenient interface we use to interact with R
- R Markdown allows use to create reproducible reports integrating code, text, 
and visualizations in a single document
- GitHub is an effective platform we will use for collaboration and version 
control

# Coming Up

- Lab on 1-22
- Complete introductory survey if you haven't already
- Ask questions!

## Lecture Notes and Exercises

First load the `tidyverse` package. A package is just a bunch of shareable code.

```{r message = FALSE}
library(tidyverse)
```

Follow the steps outlined in the slides to change "Your Name" in the header 
above to your actual name. Then, click the black arrow next to the "Knit" 
button and click "Knit to PDF".

If you are satisfied with these changes, stage, commit, and push them following
the steps in the slides.

Add a basic computation to the code chunk below (something like `2+2`). Run the
code chunk by clicking the green arrow on the right side code chunk. What do you notice?

```{r first-code-chunk}
```

## Practice

(1) Click the green arrow to run the code chunk below. You should see a 
visualization of highway miles per gallon versus displacement for 234 cars, with
points colored by the type of drive train (f = front-wheel drive, r = rear 
wheel drive, 4 = 4wd).


```{r first-visual}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point()
```

**Question:** How would you describe the relationship between type of drive 
train, displacement, and highway miles per gallon?

(2) Create new code in the code chunk below to create a scatterplot of highway miles
per galoon versus displacement with points colored by class (just replace `drv`
with `class`).

```{r second-visual}
```

**Question:** How would you describe the relationship between type of drive 
train, displacement, and highway miles per gallon?

When you are satisfied with your visualizations and answers, knit the document, 
then stage, commit, and push your changes.

### Additional Resources

- https://raw.githubusercontent.com/rstudio/cheatsheets/master/rmarkdown-2.0.pdf
- https://www.tidyverse.org/
- https://happygitwithr.com/